Death By Dropdown?

### 2025-04-01 conference-materials/2025_shiny-conf/slides.qmd
Updated Reactable Screenshots

::: {.r-stack}
![](img/reactable_example_1.png){width="75%"}
![](img/reactable_example_2.png){.fragment width="75%"}
![](img/reactable_example_3.png){.fragment width="75%"}
![](img/reactable_example_4.png){.fragment width="75%"}

<!-- Commenting to show suggestion placeholders -->
<!-- ![](img/Screenshot_examples_main_1.png){width="75%"}
![](img/Screenshot_examples_main_2.png){.fragment width="75%"}
![](img/Screenshot_examples_main_3.png){.fragment width="75%"}
![](img/Screenshot_examples_main_4.png){.fragment width="75%"} -->
:::

>>>>

::: {.r-stack style="text-align:center"}
<!-- ![](img/reactable_example_1.png){width="75%"}
![](img/reactable_example_2.png){.fragment width="75%"}
![](img/reactable_example_3.png){.fragment width="75%"}
![](img/reactable_example_4.png){.fragment width="75%"} -->

![](img/Screenshot_examples_main_1.png){width="100%"}

![](img/Screenshot_examples_main_2.png){.fragment width="100%"}

![](img/Screenshot_examples_main_3.png){.fragment width="100%"}

![](img/Screenshot_examples_main_4.png){.fragment width="100%"}

![](img/Screenshot_examples_main_5.png){.fragment width="100%"}
:::
